The Role of Variability in Learning Generalization: A Computational Modeling Approach

### 2024-05-22 Sections/IGAS.qmd
Re-add missing Procedure section; fix appendix link

### Task

The experimental task was programmed in JavaScript, using packages from the Phaser physics engine (https://phaser.io) and the jsPsych library [@deleeuwJsPsychJavaScriptLibrary2015]. The stimuli, presented on a black background, consisted of a circular blue ball -- controlled by the participant via the mouse or trackpad cursor; a rectangular green target; a red rectangular barrier located between the ball and the target; and an orange square within which the participant could control the ball before releasing it in a throw towards the target. Because the task was administered online, the absolute distance between stimuli could vary depending on the size of the computer monitor being used, but the relative distance between the stimuli was held constant. Likewise, the distance between the center of the target and the training and testing locations was scaled such that relative distances were preserved regardless of screen size. For the sake of brevity, subsequent mentions of this relative distance between stimuli, or the position where the ball landed in relation to the center of the target, will be referred to simply as distance. @fig-IGAS_Methods displays the layout of the task, as it would appear to a participant at the start of a trial, with the ball appearing in the center of the orange square. Using a mouse or trackpad, participants click down on the ball to take control of the ball, connecting the movement of the ball to the movement of the cursor. Participants can then "wind up" the ball by dragging it (within the confines of the orange square) and then launch the ball by releasing the cursor. If the ball does not land on the target, participants are presented with feedback in red text at the top right of the screen, on how many units away they were from the center of the target. If the ball was thrown outside of the boundary of the screen participants are given feedback as to how far away from the target center the ball would have been if it had continued its trajectory. If the ball strikes the barrier (from the side or by landing on top), feedback is presented telling participants to avoid hitting the barrier. If participants drag the ball outside of the orange square before releasing it, the trial terminates, and they are reminded to release the ball within the orange square. If the ball lands on the target, feedback is presented in green text, confirming that the target was hit, and presenting additional feedback on how many units away the ball was from the exact center of the target. [Link to abbrevaited example of task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.

@@

{{< include Appendix/IGAS-Supplemental.qmd >}}

>>>>

#### Task

The experimental task was programmed in JavaScript, using packages from the Phaser physics engine (https://phaser.io) and the jsPsych library [@deleeuwJsPsychJavaScriptLibrary2015]. The stimuli, presented on a black background, consisted of a circular blue ball - controlled by the participant via the mouse or trackpad cursor; a rectangular green target; a red rectangular barrier located between the ball and the target; and an orange square within which the participant could control the ball before releasing it in a throw towards the target. Because the task was administered online, the absolute distance between stimuli could vary depending on the size of the computer monitor being used, but the relative distance between the stimuli was held constant. Likewise, the distance between the center of the target and the training and testing locations was scaled such that relative distances were preserved regardless of screen size. For the sake of brevity, subsequent mentions of this relative distance between stimuli, or the position where the ball landed in relation to the center of the target, will be referred to simply as distance. @fig-IGAS_Methods displays the layout of the task, as it would appear to a participant at the start of a trial, with the ball appearing in the center of the orange square. Using a mouse or trackpad, participants click down on the ball to take control of the ball, connecting the movement of the ball to the movement of the cursor. Participants can then "wind up" the ball by dragging it (within the confines of the orange square) and then launch the ball by releasing the cursor. If the ball does not land on the target, participants are presented with feedback in red text at the top right of the screen, specifying how many scaled units away the ball was from the center of the target. If the ball was thrown outside of the boundary of the screen participants are given feedback as to how far away from the target center the ball would have been if it had continued its trajectory. If the ball strikes the barrier (from the side or by landing on top), feedback is presented telling participants to avoid hitting the barrier. If participants drag the ball outside of the orange square before releasing it, the trial terminates, and they are reminded to release the ball within the orange square. If the ball lands on the target, feedback is presented in green text, confirming that the target was hit, and presenting additional feedback on how many units away the ball was from the exact center of the target.

[Link to abbreviated example of task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.

@@

{{< include /Sections/Appendix/IGAS-Supplemental.qmd >}}

### 2024-05-22 Sections/full.qmd
Re-add missing Procedure section; fix appendix link

---
title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
author:
- name: Thomas Gorman
  affiliation: Indiana University
page-layout: full
code-fold: true
code-tools: true
toc: true
toc-location: body
toc-depth: 4
cache: true
format-links: [hikmah-manuscript-pdf, gfm, docx]
execute: 
  warning: false
  eval: true
format:
  html: default
  hugo-md:
    echo: false
    include: true
    html-math-method: mathjax
    output-file: diss_full_hugo.md
  gfm:
    echo: false
    #output: false
    output-file: diss_full_gfm.md
  hikmah-manuscript-pdf:
    echo: false
    output-file: "tg_full_disser.pdf"
    mainfont: "Linux Libertine O"
    mainfontoptions:
      - "Numbers=Proportional"
      - "Numbers=OldStyle"
    mathfont: "Libertinus Math"
  docx:
    echo: false
    prefer-html: true
    output-file: "TG_Full_Dissert.docx"
    toc: true
prefer-html: true
---

@@

{{< include pre_sections/toc_pdf.qmd >}}

@@

#options(brms.backend="cmdstanr",mc.cores=4)
initial_contrasts <- options("contrasts")$contrasts
options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, contrasts = c("contr.sum", "contr.poly"))
defaultContrasts = options()$contrasts

@@

[Apppendix](Appendix/Full_Appendix.qmd) available at tegorman13.github.io/Dissertation/Sections/Appendix.html

# References

>>>>

---
title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
author:
- name: Thomas Gorman
  affiliation: Indiana University
  affiliation-url: https://psych.indiana.edu/
  url: https://tegorman13.github.io/
  orcid: 0000-0001-5366-5442
page-layout: full
code-fold: true
code-tools: true
toc: true
toc-location: body
toc-depth: 4
cache: true
format-links: [hikmah-manuscript-pdf, gfm, docx]
execute: 
  warning: false
  eval: true
format:
  html: default
  hugo-md:
    echo: false
    include: true
    html-math-method: mathjax
    output-file: diss_full_hugo.md
  gfm:
    echo: false
    #output: false
    output-file: diss_full_gfm.md
  hikmah-manuscript-pdf:
    echo: false
    output-file: "tg_full_disser.pdf"
    mainfont: "Linux Libertine O"
    mainfontoptions:
      - "Numbers=Proportional"
      - "Numbers=OldStyle"
    mathfont: "Libertinus Math"
  docx:
    echo: false
    prefer-html: true
    output-file: "TG_Full_Dissert.docx"
    toc: true
prefer-html: true
---

@@

{{< include /Sections/pre_sections/toc_pdf.qmd >}}

@@

#options(brms.backend="cmdstanr",mc.cores=4)
initial_contrasts <- options("contrasts")$contrasts
options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, contrasts = c("contr.sum", "contr.poly"))
#defaultContrasts = options()$contrasts

@@

[Apppendix](https://tegorman13.github.io/Dissertation/Sections/Appendix/Full_Appendix.html) available at https://tegorman13.github.io/Dissertation/Sections/Appendix/Full_Appendix.html

# References
::: {#refs}
:::
